Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-03-07 docs/supplement.Rnw
included briers in micrornaseq_cervical_cancer.R

  \section{Application to MicroRNAs in colorectal cancer}\label{sec:colorectal}
  \subsection{Additional comparisons}
  We compared \texttt{gren} to two methods in addition to the ones in the MD: 
  the sparse group lasso (\texttt{SGL}) by \cite{simon_sparse-group_2013} and 
  the group exponential lasso (\texttt{gel}) by \cite{breheny_group_2015}. For
  all methods with a tuning parameter $\alpha$, we set 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$ and present the AUC on the test set in 
  Figure \ref{fig:lines_micrornaseq_colorectal_cancer_res1_auc}.
<<lines_micrornaseq_colorectal_cancer_res1_auc, fig.cap="Estimated AUC for the colorectal cancer example.", out.width="100%", fig.asp=1>>=
@

>>>>

  \section{Application to MicroRNAs in colorectal cancer}\label{sec:colorectal}
  \subsection{Additional comparisons}
  We compared \texttt{gren} to two methods in addition to the ones in the MD: 
  the sparse group lasso (\texttt{SGL}) by \cite{simon_sparse-group_2013} and 
  the group exponential lasso (\texttt{gel}) by \cite{breheny_group_2015}. For
  all methods with a tuning parameter $\alpha$, we set 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$ and present the AUC and Brier skill score 
  on the test set in Figures 
  \ref{fig:lines_micrornaseq_colorectal_cancer_res1_auc}--
  \ref{fig:lines_micrornaseq_colorectal_cancer_res1_briers}.
<<lines_micrornaseq_colorectal_cancer_res1_auc, fig.cap="Estimated AUC for the colorectal cancer example.", out.width="100%", fig.asp=1>>=
@

<<lines_micrornaseq_colorectal_cancer_res1_briers, fig.cap="Estimated Brier skill score for the colorectal cancer example.", out.width="100%", fig.asp=1>>=
@
